\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-07-16 response.tex

\textbf{We have begun to extend the correlation analysis between within-clade antigenic drift and multiple measures of influenza incidence, including ILI, virus isolation, excess P\&I mortality and influenza-associated hospitalization rates. This analysis is also attempting to look at a finer temporal scale, rather than the course-grained 1-year bins in the current study and attempting to better match geographic bounds in antigenic and incidence data.  This said, we believe that further extending the incidence correlation requires a separate publication to  describe adequately, and is beyond the scope of the current analysis.}

The ``uninformed'' prior used in Table 1 is not described in detail, but it actually hides a subtle issue. For an unbounded variable like the x- and y- positions of a mapped isolate, the ``uninformed'' prior cannot simply be uniform on $R^2$, but rather is uniform on some compact subset of $R^2$. In other words, the authors had to assume a prior with a maximum possible x- and y-position. They don't describe what maximum bounds went into their ``uniformed'' prior, but this is well-known to influence the results of Bayesian analyses in general. This is a relatively minor issue -- authors should simply show how the form of his uniformed prior influences the resulting maps.

The authors should add a column to Table 1 showing the performance of the best possible model arising from purely genetic data -- that is, 2-D or 3-D embeddings based on aa hamming distances alone, ignoring all HI data.

\textbf{We agree that it would be ideal to provide a test error associated with a purely genetic model.  However, test errors in Table 1 are based on the prediction of a set of HI titers based on other HI titers or other HI titers plus genetic data.  Without including some form of HI information, it's difficult to see how to predict HI titer.  One could have a `distance' in terms of AA rather than antigenic map units, but in this case, one would still need to include a scaling for `serum effects', which could not be made without reference to HI data.  Regardless, we've attempted to address this issue in our discussion of correlation between antigenic and genetic distances, as described above.}

### 2013-07-23 flux.tex
Small notation fix (change \mu to m in diffuse normal mean).

We calculate the overall likelihood by multiplying probabilities of individual measurements
\begin{equation}  \label{bmds}
	L(\viruses,\sera) = \prod_{(i,j) \in \cal I} f(H_{ij}),
\end{equation}
using probability functions $\point$, $\threshold$ and $\interval$ as appropriate.
We begin by assuming independent, diffuse normal priors on virus and serum locations
\begin{eqnarray}
	\virus_i &\sim& \mathrm{Normal}(\boldsymbol{\mu},\boldsymbol{\Sigma}) \nonumber \\
	\serum_j &\sim& \mathrm{Normal}(\boldsymbol{\mu},\boldsymbol{\Sigma}),
\end{eqnarray}
where $\boldsymbol{\mu} = (0,\ldots,0)^{\prime}$ and $\boldsymbol{\Sigma}$ is a diagonal matrix with diagonal elements all equal to $10000$.

>>>>

We calculate the overall likelihood by multiplying probabilities of individual measurements
\begin{equation}  \label{bmds}
	L(\viruses,\sera) = \prod_{(i,j) \in \cal I} f(H_{ij}),
\end{equation}
using probability functions $\point$, $\threshold$ and $\interval$ as appropriate.
We begin by assuming independent, diffuse normal priors on virus and serum locations
\begin{eqnarray}
	\virus_i &\sim& \normal(\mathbf{m},\boldsymbol{\Sigma}) \nonumber \\
	\serum_j &\sim& \normal(\mathbf{m},\boldsymbol{\Sigma}),
\end{eqnarray}
where $\mathbf{m} = (0,\ldots,0)^{\prime}$ and $\boldsymbol{\Sigma}$ is a diagonal matrix with diagonal elements all equal to $10000$.
